### 2021-12-23 paper/manuscript.Rmd
quietstart [ci skip]

  Enter author note here.

>>>>

  Author contributions: CvL conceived of the method; wrote simulation, analysis,
  and package code; and drafted the manuscript. SE implemented the method in
  stan and contributed package code; contributed paragraphs and revised the
  manuscript. EC wrote manuscript outline and contributed paragraphs; curated
  existing lab notes; conducted literature research; performed initial analyses.
